|

### 2021-02-14 appendix/appendix.Rmd
add seeded lda model

\footnotesize
```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=8, fig.height=5.6, fig.pos="H"}
# Latent Dirichlet allocation
tmod_lda <- textmodel_lda(dfmat, k = 3)
terms(tmod_lda, 10)
table(topics(tmod_lda))
```
\normalsize

>>>>

\footnotesize
```{r conjoint-lda, warning=F, message=F, error=F, cache=T, fig.width=10, fig.height=9, fig.post="H"}
# Unsupervised LDA
tmod_lda <- textmodel_lda(dfmat, k = 3)
terms(tmod_lda, 10)
table(topics(tmod_lda))
```
\normalsize

Our last model is a semisupervised LDA, in which we include a series of
keywords to measure how frequently some pre-defined topics appear often in the
responses. We adopt a conservative approach and only include words that we have
a high degree of confidence that are not ambiguous. There are four pre-defined
topics in this estimation. The first refers to victims, and include words for
children, life, and victim (along with possible variations). The second topic
describes crime characteristics with words such as murder, rape, kill, molest,
and steal. The next group has four keywords that describe lynching
perpetrators, and they are gangs, family, bystanders, and police. The fourth
topic includes terms to identify respondents who are against lynchings, and we
added against, none, do not agree, and choice as the seed terms. We see that
these groups have a large number of terms each, and that crime characteristics
is the topic that shows more often when our terms are applied.

\footnotesize
```{r conjoint-seededlda, warning=F, message=F, error=F, cache=T, fig.width=15, fig.height=9, fig.pos="H"}
# Semisupervised LDA
keywords <- dictionary(list(Victim      = c("crian*", "vida*", "v*tima*"),
                            Crime       = c("assassin*", "estupr*", "mata*", "molest*", "roub*"),
                            Perpetrator = c("gang*", "fam*lia*", "pedestr*", "pol*cia*"),
                            Against     = c("contra", "nenhum*", "n*o concord*", "op**o")))

slda <- textmodel_seededlda(dfmat, keywords, residual = TRUE)
terms(slda, 10)
table(topics(slda))
```
\normalsize
